### 2021-05-19 project_ashish_monograph/syst.tex
updated

8. Cross-detector comparisons: After corrections of out-of-time effects and efficiency changes monitored by emittance scans, residual effects are evaluated by cross-detector comparison.                    \\

8. Afterglow effects: A small out of time response appears in unfilled bunches after colliding bunches. These effects are described in detail in the previous section \cite{CMS-PAS-LUM-18-002}.

>>>>

8. Afterglow effects: A small out of time response appears in unfilled bunches after colliding bunches. These effects are described in detail in the previous section. \\

9. Cross-detector comparisons: After corrections of out-of-time effects (afterglow), stability and linearity are applied, luminosity measurement from various detector like BCM1F, PLT and HFOC can be compared to do very precise luminosity determination by taking into account exact corrections \cite{CMS-PAS-LUM-18-002}.
